MADA Project Manuscript

### 2021-10-29 products/manuscript/Manuscript.Rmd
Added titles to each figure for part 3

>>>>

We can see with looking at figure 8 that the percentage of cases are extremely right skewed. For now, I will proceed with doing some simple linear regression. Below shows model statistics for each model and a visual showing the relationship between the two variables.

Figure 10 is showing statistics for the predictor vaccine percentage.
```{r vaccine pct,  echo=FALSE}
knitr::include_graphics("../../results/figure10.png")

tab9=readRDS("../../results/tablevacc2.rds")
knitr::kable(tab9)
```

Figure 11 is showing statistics for the predictor health care funds.
```{r health care,  echo=FALSE}
knitr::include_graphics("../../results/figure11.png")

tab10=readRDS("../../results/tablehc2.rds")
knitr::kable(tab10)
```

Figure 12 is showing statistics for the predictor number of tests per person.
```{r Tests,  echo=FALSE}
knitr::include_graphics("../../results/figure12.png")

tab11=readRDS("../../results/tabletests2.rds")
knitr::kable(tab11)
```

Figure 13 is showing statistics for the predictor location which specifies the continent for each country.
```{r Location,  echo=FALSE}
knitr::include_graphics("../../results/figure13.png")

tab12=readRDS("../../results/tableloc2.rds")
knitr::kable(tab12)
```

From these visuals, we can see that the R^2's for these models are still relatively low but a simple linear regression of using percent vaccination or the location of each country have R^2's of around 0.35 which is an improvement from the linear regression models from using logit transformation of difference in proportions as the outcome.
